\\Large The heat is on: Rising temperatures alter when, how, and where large terrestrial mammals move

### 2025-09-03 writing/appendix-b-gams.Rmd
added note on BC albers projection in fig cap

```{r resources, fig.cap="Resource rasters used for each species' hierarchical resource selection function."}
knitr::include_graphics('../figures/local-resources.png')
```

>>>>

```{r resources, fig.cap="Resource rasters used for each species' hierarchical resource selection function. All maps are shown in the BC Albers Equal Area Conic projection (EPSG:3005)."}
knitr::include_graphics('../figures/local-resources.png')
```
